---
title: "linear models"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
library(mgcv)
library(modelr)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%",
  warning = FALSE,
  message = FALSE)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## step one 
```{r}
nonlin_df = 
  tibble(
    id = 1:100,
    x = runif(100, 0, 1),
    y = 1 - 10 * (x - .3) ^ 2 + rnorm(100, 0, .3)
  )

nonlin_df %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point()
```

Let's get this by hand

```{r}
train_df = sample_n(nonlin_df, 80)
test_df = anti_join(nonlin_df, train_df)
```

```{r}
train_df %>% 
  ggplot(aes(x = x, y =y)) + 
  geom_point() + 
  geom_point(data = test_df, color = "red")
```

## Three Models 

```{r}
linear_mod = lm(y~x, data = train_df)
smooth_mod = mgcv::gam(y ~ s(x), data = train_df)
wiggly_mod = mgcv::gam(y ~ s(x, k = 30), sp = 10e-6, data = train_df)
```

```{r}
train_df %>% 
  add_predictions(smooth_mod) %>% 
  ggplot(aes(x = x, y = y)) + geom_point() + geom_line(aes(y = pred), color = "red") + geom_point(data = test_df, color = "red")
```

##Let's make predictions and compute RMSEs
comparing red line and red points above 
```{r}
rmse(linear_mod, test_df)
rmse(smooth_mod, test_df)
rmse(wiggly_mod, test_df)
```

## can we iterate ..?
```{r}
cv_df =
  crossv_mc(nonlin_df, 100)

cv_df %>% pull(train) %>% .[[1]] %>% as_tibble

cv_df %>% pull(test) %>% .[[1]] %>% as_tibble()

```

## Generate multi train and test dataset
1. add models to each row of training dataset
2. add rmse to each model
3. might make a boxplot of rmse following the data
```{r}
cv_df = cv_df %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  ) %>% 
  mutate(
    linear_fits = map(.x = train, ~lm(y ~ x, data = .x)),
    smooth_fits = map(.x = train, ~mgcv::gam(y ~ s(x), data = .x))
  ) %>% 
  mutate(
    rmse_linear = map2_dbl(.x = linear_fits, .y = test, ~rmse(model = .x, data = .y)),
    rmse_smooth = map2_dbl(.x = smooth_fits, .y = test, ~rmse(model = .x, data = .y))
  )

cv_df
```


Make a boxplot 

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  ggplot(aes(x = model, y = rmse)) +
  geom_boxplot()
```
## Child Growth Example

```{r}
child_growth = read_csv("./data/nepalese_children.csv")
```

```{r}
child_growth %>% 
  ggplot(aes(x = weight, y = armc)) + geom_point(alpha = .3)
```

Piecewise linear models 
```{r}
child_growth = 
  child_growth %>% 
  mutate(
    weight_pwl = (weight > 7) * (weight - 7) 
  )
```


```{r}
linear_model = lm(armc ~ weight, data = child_growth)
pwl_model = lm(armc ~ weight + weight_pwl, data = child_growth)
smooth_model = mgcv::gam(armc ~ s(weight), data = child_growth)
```

show change of linear model before and after weight=7
```{r}
child_growth %>% 
  add_predictions(pwl_model) %>% 
  ggplot(aes(x = weight, y = armc)) +
  geom_point(alpha = .3) +
  geom_line(aes(y = pred), color = "red")
```
```{r}
child_growth %>% 
  add_predictions(smooth_model) %>% 
  ggplot(aes(x = weight, y = armc)) +
  geom_point(alpha = .3) +
  geom_line(aes(y = pred), color = "red")
```

```{r}
cv_df = 
  crossv_mc(child_growth, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  )
```

```{r}
cv_df = cv_df %>% 
  mutate(
    linear_fits = map(.x = train, ~lm(armc ~ weight, data = .x)),
    pwl_fits = map(.x = train, ~lm(armc ~ weight + weight_pwl, data = .x)),
    smooth_fits = map(.x = train, ~mgcv::gam(armc ~ s(weight), data = .x))
  ) %>% 
  mutate(
    rmse_linear = map2_dbl(.x = linear_fits, .y = test, ~rmse(model = .x, data = .y)),
    rmse_pwl = map2_dbl(.x = pwl_fits, .y = test, ~rmse(model = .x, data = .y)),
    rmse_smooth = map2_dbl(.x = smooth_fits, .y = test, ~rmse(model = .x, data = .y))
  )
```

look into results 

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  ggplot(aes(x = model, y = rmse)) +
  geom_boxplot()
```

