---
title: "listcolumn"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)

set.seed(1)
library(rvest)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%",
  warning = FALSE,
  message = FALSE)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## lists
```{r}
vec_numeric = 5:8
vec_char = c("My", "name", "is", "Jeff")
vec_logical = c(TRUE, TRUE, TRUE, FALSE)
```
 
```{r}
l = list(
  vec_numeric = 5:8,
  mat = matrix(1:8,2,4),
  vec_logical = c(TRUE, FALSE),
  summary = summary(rnorm(1000))
)

l
```
accessing list items

```{r}
l$vec_numeric

l[[3]]
```
## loops

write a 'for' loop

```{r}
list_norm = list(
  a = rnorm(20,5,4),
  b = rnorm(20, 0, 5),
  c = rnorm(20, 10, .2),
  d = rnorm(20, -3, 1)
)
```

```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)

  tibble(
    mean = mean_x, 
    sd = sd_x
  )
}
```

```{r}
output = vector("list", length = 4)

for (i in 1:4) {
  output[[i]] = mean_and_sd(list_norm[[i]])
}

output[[1]]
output
```

## can we map 

```{r}
map(list_norm, mean_and_sd)
```

what about other functions
```{r}
map(list_norm, summary)
```

map variants
```{r}
map_dbl(list_norm, median)
map_df(list_norm, mean_and_sd)
```

## list columns 

```{r}
listcol_df = 
  tibble(
    name = c("a", "b", "c",  "d"),
    norm = list_norm
  )

listcol_df[["norm"]]

map(listcol_df[["norm"]], mean_and_sd)
```

can we add list columns 

```{r}
listcol_df %>% 
  mutate(
    m_sd = map_df(norm, mean_and_sd) 
  ) %>% 
  select(-norm)
```

## revisit weather dataset

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(  
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

let's nest within weather stations...

```{r}
weather_nest_df =
  weather_df %>% 
  nest(data = date:tmin)
```

really is a list column

```{r}
weather_nest_df[["data"]]
```


take the central park data and do linear regression
```{r}
weather_nest_df[["data"]][[1]]

lm(tmax ~ tmin, data = weather_nest_df[["data"]][[1]])
```

 lets write a short lil ol function
 
```{r}
weather_lm = function(df) {
  lm(tmax ~ tmin, data = df)
}

map(weather_nest_df[["data"]], weather_lm)
```
 
 can i do all this in a tidy way
 
```{r}
weather_nest_df %>% 
  mutate(
    model = map(data, weather_lm)
  )
```
 
 unnesting
 
```{r}
weather_nest_df %>% 
  unnest(data)
```
 
## Napoleon!

here's my scraping function that works for a single page

```{r}
read_page_reviews <- function(url) {
  
  html = read_html(url)
  
  review_titles = 
    html %>%
    html_nodes(".a-text-bold span") %>%
    html_text()
  
  review_stars = 
    html %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text() %>%
    str_extract("^\\d") %>%
    as.numeric()
  
  review_text = 
    html %>%
    html_nodes(".review-text-content span") %>%
    html_text() %>% 
    str_replace_all("\n", "") %>% 
    str_trim() %>% 
    str_subset("The media could not be loaded.", negate = TRUE) %>% 
    str_subset("^$", negate = TRUE)
  
  tibble(
    title = review_titles,
    stars = review_stars,
    text = review_text
  )
}
```

```{r}
url_base = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="
vec_urls = str_c(url_base, 1:5)
```

```{r}
map(vec_urls, read_page_reviews)

napoleon_reviews =
  tibble(
    page = 1:5,
    page_url = str_c(url_base, page)
  ) %>% 
  mutate(
    reviews = map(page_url, read_page_reviews)
  )

napoleon_reviews %>% 
  select(-page_url) %>% 
  unnest(reviews)
```


```{r}
output = vector("list", 5)

for (i in 1:5) {
  output[[i]] = read_page_reviews(vec_urls[[i]])
}

dynamite_reviews = bind_rows(output)

dynamite_reviews = map_df(vec_urls, read_page_reviews)
```

  
  
  